Learning and Reputation under Monopoly and Duopoly: \\A Competing Bandits Approach

### 2018-08-16 paper/competing_bandits.tex
cosmetics

\begin{figure}
\caption{Relative Reputation Plots}
\includegraphics[scale=0.35]{figures/relative_uniform_annotated_plot}
\includegraphics[scale=0.35]{figures/ts_dg_nih_10_prelim}
\caption*{The plots contain the average reputation over $1000$ runs for a memory size of $100$ where, for a given $t$, we record the reputation of both of the algorithms on a given instance and then calculate the proportion of runs where $TS \geq DG$. The shaded area display 95\% confidence intervals.}
\label{relative_rep_plots}

>>>>

\begin{figure}
\caption{Relative Reputation Plots}
\includegraphics[scale=0.35]{figures/relative_uniform_annotated_plot}
\includegraphics[scale=0.35]{figures/ts_dg_nih_10_prelim}
\caption*{\tiny{The plots contain the average reputation over $1000$ runs for a memory size of $100$ where, for a given $t$, we record the reputation of both of the algorithms on a given instance and then calculate the proportion of runs where $TS \geq DG$. The shaded area display 95\% confidence intervals.}}
\label{relative_rep_plots}
